Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA

### 2022-09-01 src/tex/ms.tex
text edits

\shorttitle{Applying a metallicity-dependent binary fraction to DWD formation}
\shortauthors{Thiele, Breivik, \& Sanderson}

@@

\author[0000-0001-7442-6926]{Sarah Thiele}
\affiliation{Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC, V6T 1Z1, Canada}
\affiliation{Canadian Institute for Theoretical Astrophysics, University
of Toronto, 60 St. George Street, Toronto, Ontario, M5S 1A7,
Canada}
\author[0000-0001-5228-6598]{Katelyn Breivik}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
\affiliation{Canadian Institute for Theoretical Astrophysics, University
of Toronto, 60 St. George Street, Toronto, ON, M5S 1A7,
Canada}
\author[0000-0003-3939-3297]{Robyn E. Sanderson}
\affiliation{Department of Physics and Astronomy, University of Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}

% Abstract with filler text
\begin{abstract}
Short-period double white dwarf (DWD) binaries will be the most prolific source of gravitational waves (GWs) for the Laser Interferometer Space Antenna (LISA). DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by overlapping GW signals, limiting the detectability of individual sources of all kinds. Population modeling of Galactic DWDs typically assumes a binary fraction of $50\%$ \textbf{and a log-uniform Zero Age Main Sequence (ZAMS) orbital period distribution}. However, recent observations have shown that the binary fraction of close, solar-type stars exhibits a strong anti-correlation with metallicity \textbf{which modulates the ZAMS orbital period distribution below $10^4$ days}. In this study we perform the first simulation of the Galactic DWD population observable by LISA which incorporates an empirically-derived metallicity-dependent binary fraction. We simulate DWDs using the binary population synthesis suite \cosmic\ and incorporate a metallicity-dependent star formation history to create a Galactic population of short-period DWDs. We compare two models: one which assumes a metallicity-dependent binary fraction \textbf{and ZAMS orbital period distribution}, and one with a binary fraction of 50\% \textbf{and log-uniform ZAMS orbital period distribution}. \textbf{We repeat our analysis for three different assumptions for Roche-lobe overflow interactions.} We find that while metallicity impacts the evolution and intrinsic properties of our simulated DWD progenitor binaries, the LISA-resolvable populations of the two models remain roughly indistinguishable. However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction \textbf{for two of our four variations.} This effect lowers the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources. \textbf{The LISA population remains unchanged in number for two variations, highlighting the sensitivity of the population to binary evolution prescriptions.} %KB: I think this is a good choice!\textbf{Strikeout: [\emph{We repeat our analysis for three different assumptions for Roche-lobe overflow interactions and find the population reduction to be robust when a metallicity-dependent binary fraction is assumed.}]}
\end{abstract}

@@

\textbf{Figure \ref{fig:met_dep_porb}, shows the companion frequency f$_{\rm{logP}}$ for solar-type stars as a function of the logarithm of orbital period, mirroring the inner binaries curve of Figure 2 in \citet{Moe2021} and scaling to an overall multiplicity frequency of 0.67 (equivalent to an integrated binary fraction of 50\%) at solar metallicity. To obtain the normalization of the companion frequency for close binaries (P$_{\rm{orb}}<10^4$),} we fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and \text{close} binary fraction $f_{\rm{b}}$ as

@@

\textbf{We count all higher-order companions as secondary, or binary, components. We show curves for all 15 of our metallicity bins, increasing in metallicity from darkest to lightest curve colour. The lowest metallicity ([Fe/H]=-2.3) shows the highest propensity for short-period binaries, in contrast to higher metallicity systems which have a frequency distribution that has a relatively constant companion frequency for orbital periods between $10^4$ and $10^6$ days.}

\textbf{While we simulate binaries across the entire orbital period distribution, the close binary fraction, which exhibits the discussed metallicity dependence, will be that which impacts the LISA population as systems with $\log_{10}(\rm{P}_{\rm{orb}}/$day)$>4$ will be unlikely to evolve enough to enter the LISA band by present day.}

@@

The metallicity-dependent \textbf{close} binary fraction \textbf{for solar-type binaries (P $< 10^4$ days), or simply the close binary fraction from here on, }% S: Should I change all instances of "binary fraction" to "close binary fraction" then? %KB: I will keep an eye out to make the changes
is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid. The \textbf{close} binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly. These two opposing trends compete throughout this study along with the impact of metallicity on single star evolution to form the final numerical distribution of systems in our DWD populations.

@@

\noindent where $h_c$ is the characteristic strain of the system, $S_n(f)$ is the LISA sensitivity curve of \citet{Robson2019}, and the frequency limits are determined by the orbital evolution over the observation time, $T_{\rm{obs}}=4\,\rm{yr}$. The characteristic strain for %DWDs 
circular orbits is 
\begin{equation}
    h_{c}^2 = \frac{2^{2/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}},
\end{equation}
\noindent where $\mathcal{M}_c = (M_1M_2)^{3/5}/(M_1 + M_2)^{1/5}$ is the system's chirp mass, and $D_L$ is the systems luminosity distance which we assume to be the distance of each simulated DWD to the Sun.

@@

The Galactic foreground included in the \citet{Robson2019} LISA noise curve was generated using a different binary evolution code and set of model assumptions for DWD formation and evolution \citep{Toonen2012, Korol2017}. Thus, we use the detector curve only and generate an approximate foreground from each of our populations as follows. Instead of performing a full source subtraction algorithm \citep[e.g.][]{Littenberg2020}, which is out of the scope of this work, we calculate the PSD of the Galactic DWD population with a frequency resolution set by the LISA mission time as $1/T_{\rm{obs}}\sim1/4\,\rm{yr}^{-1}\sim8\times10^{-9}\,\rm{Hz}$. We then approximate the foreground as the running median of the PSD with a boxcar window with a width of $10^3$ frequency bins similar to \citet{Benacquista2006}. The Galactic DWD PSD is truncated near $10\,\rm{mHz}$ for both of our models because we remove all DWDs which experience Roche-lobe overflow. In order to smooth the effect of this truncation in our foreground, we fit each running median with fourth-order polynomials for GW frequencies up to $1\,\rm{mHz}$, thus allowing an approximation of the foreground PSD for higher frequencies. These fits are listed in Table~\ref{tbl:fits} where the polynomial is described as
\begin{equation}
\label{eq:fit}
    \log_{10}(\rm{confusion\ fit}/\rm{Hz}) = a\,x^4 + b\,x^3 + c\,x^2 + d\,x + e
\end{equation}
\noindent and $x=\log_{10}(f_{\rm{GW}}/\rm{Hz})$. We add the fitted polynomial of the PSD's running median to the LISA noise PSD to obtain a sensitivity curve for each model \textbf{and variation}.

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/form_eff.pdf}
    \caption{The DWD formation efficiency vs metallicity of DWD populations simulated with \cosmic. Each panel shows the formation efficiency for a given DWD type \textbf{and variation}. The solid lines indicate the formation efficiency for model FZ which incorporates a metallicity-dependent binary fraction. The dashed lines indicate the formation efficiency for model F50, which assumes a constant binary fraction of $50\%$. The DWD formation efficiency drops by a factor of $4-5$ for model FZ and a factor of %\textbf{\sout{2-5} 
    \textbf{1-5} for model F50. See Section~\ref{sec:formeff} for a careful description of the trends for each DWD type.}
    \label{fig:form_eff}
    \script{form_eff.py}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/CEsep.pdf}
    \caption{Average interaction separation, $\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type \textbf{and variation} from model FZ. Solid lines show the average separation at the first RLO for binaries in each metallicity bin. The shaded regions show the $1\sigma$ spread around the mean within each metallicity bin. The average interaction separation increases with metallicity for every DWD type\textbf{, except for $\alpha5$ which remains approximately constant for CO + He and ONe + X}. The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts. The sharp drop of the CO + CO average at the highest-metallicity bin \textbf{of the fiducial variation} is due to binning effects of the figure: it only contains 115 systems, of which the majority stem from a single low-separation system which was sampled 94 times times during the simulation. \textbf{The regions of metallicity where there is not shading beyond the mean trend are also due to low numbers of DWDs in each bin}.} 
    \label{fig:CEsep}
    \script{CEsep.py}
\end{figure*}

For short-period CO + He DWD progenitor binaries with orbital periods below $\sim30~\rm{days}$, the only channel for \kb{stellar} mergers before DWD formation is during a CE evolution. This channel is similar to the stellar merger channel for He + He DWDs, but due to higher-mass progenitors the CE evolution results in the binary component with a higher mass becoming a CO WD. At higher metallicities, the CO WD merges with its companion. Higher-metallicity progenitors have a larger fraction of their mass in the convective envelope when compared to lower-metallicity stars of the same mass \citep{Amard2019, Amard2020}. Thus a CE phase with a higher-metallicity progenitor requires more orbital energy to eject the common envelope, causing a larger amount of orbital shrinking which results in a merger later in its binary evolution.

For CO + He DWD progenitor systems with intermediate orbital periods ($1.5\leq \log_{10}(P_{\rm{orb}}/\rm{day})< 2.5$) the mechanisms which impact formation efficiency are complex. The dominant way to % R: lose
\textbf{not form} CO + He DWDs is stellar mergers that occur during the second CE phase. For lower-metallicity systems, the second CE is successful, while the opposite is true for higher-metallicity systems. This is again because the envelope mass of the CE evolution donor at higher metallicity is larger than it would be at lower metallicity and thus requires more orbital energy to eject in the CE phase. This leads to shorter post-CE orbital periods after the first CE phase and hence mergers during the second phase.

@@

\textbf{For binary systems leading to He + He DWDs, there are many more mergers for $\alpha25$ than for the fiducial variation. The lower CE efficiency leads to DWD progenitor mergers from failed CE ejection, or the CE shrinking the orbit such that it then merges on the second CE phase. Because there are more ZAMS binaries with orbital periods shorter than $10^4$ days in F50, as the population evolves there are more likely to be binary interactions in the population for F50 than FZ. This leads to more mergers in $\alpha25$ occurring for F50 before formation of the DWD and thus a lower formation efficiency overall for F50 in contrast to FZ. This is illustrated in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}. Similar to the fiducial parameter variation, a binary that becomes a He + He DWD at lower metallicities would merge before becoming one at higher metallicities because of the longer evolution timescales. These later interactions lead to closer post-CE separations and thus more mergers. The dip at [Fe/H] $\simeq -1.5\%$ stems from mergers before the DWD forms, again similar to the fiducial parameter variation. The peak that occurs in $\alpha25$ at $\sim 10\%$ Z$_\odot$ arises from binaries evolving faster and thus interacting earlier as metallicity increases. This means that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive to produce a He + He DWD. At higher metallicities, there are a higher proportion of wide ZAMS binaries, which evolve off the Main Sequence too slowly to form a He + He DWD, causing the efficiency drop.}

@@

\textbf{Beyond the effects described above, the efficiency drop across metallicity is similar to the fiducial parameter variation in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and in the change of formation channel for different period ranges across metallicity. We find the highest formation efficiency for variation $q3$. Only the shortest-period binaries do not form a DWD through mergers at higher metallicities. At low metallicities, even binaries with ZAMS orbital periods P$_{\rm{orb}}\lesssim 100$ days form He + He DWDs, with binaries in model FZ reaching ZAMS orbital periods less than a day in length. This leads to a higher formation efficiency from F50 over FZ for parameter variation $q3$ because of the higher number of shortest-period ZAMS binaries in the log-uniform distribution of F50.}

\textbf{For CO + He binaries, there are again many more mergers for parameter variation $\alpha25$ relative to the fiducial case. This is the dominant way that progenitors do not evolve to produce DWDs at higher metallicities. At low metallicities, a number of progenitor binaries form CO + CO DWDs instead of He + CO DWDs. This is especially the case in near $\log_{10}$(Z/Z$_\odot)\sim -2$, where RLO occurs late enough in a binary's evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence producing a dip in the formation efficiency. Because parameter variation $\alpha5$ leads to less mergers due to the high CE efficiency, the formation efficiency is mostly governed by the metallicity-dependent ZAMS orbital period distribution. At higher metallicities the majority of cases in model FZ where progenitors don't produce a CO + He DWD are due to progenitor mergers or to He + He DWDs forming instead of CO + He DWDs.} %due to the faster evolution at high metallicities and increasing radii inducing earlier binary interactions and hence stripping of both star's envelopes [$\leftarrow$ is this correct logic?]. I think this is already discussed above for fiducial so we don't need to worry about it.
\textbf{At higher metallicities, the ZAMS orbital period distribution of FZ also drops below the orbital period distribution of F50 and extends out to orbital periods beyond what would form a CO + He. This causes the formation efficiencies for FZ and F50 to cross at log$_{10}$(Z/Z$_\odot$)$\sim-0.5$. This is also apparent for the $q3$ variation, and to a lesser extent in the fiducial case.} %Any lost systems in $q3$ also is contributed to by: (i) some binaries at high metallicities not forming a CO + He DWD by present day due to envelope-stripping timescales being delayed by phases of stable mass transfer, (ii) mergers, and (ii) ONe + X DWDs forming instead.
\textbf{In $q3$, for any given orbital period we find that lower mass DWDs originate from lower metallicities, thus leading to an approximately constant formation efficiency.}

\textbf{For CO + CO, across all variations, very close ZAMS binaries (P$_{\rm{orb}}\sim\mathcal{O}(100$ days)) at high metallicities form a CO + He or He + He DWD instead of a CO + CO because the binary interacts before core Helium burning of one or both components. } 
%lost at high metallicities when a binary that would form a CO + CO at low metallicities forms a CO + He or He + He DWD instead 
\textbf{There are again many more mergers in $\alpha25$, and fewer mergers for $\alpha5$. Due to the high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods survive to become CO + CO DWDs rather than merging or becoming CO + He or He + He DWDs. There are less fewer mergers overall for $q3$ than all the $\alpha$ variations because the first RLO occurrence leads to stable mass transfer from the primary to the secondary rather than multiple CE phases. For both the $\alpha5$ and $q3$ variations, the majority of CO + CO DWDs originate in wide enough orbits that they don't interact before DWD formation. This leads to an approximately constant formation efficiency across metallicity in both cases.}

\textbf{For model FZ, the ONe + X formation efficiencies follow similar trends aross each parameter variation. Their formation scenarios are similar to those described above for the fiducial binary evolution parameter set. The main difference between each parameter variation is only in the number of sources produced since the number of stellar mergers that occur before DWD formation increases with decreasing common envelope efficiency. In model F50, the formation efficiency is decreased significantly for parameter variation $\alpha25$ because the log-uniform orbital period distribution produces many ZAMS binaries with very short orbital periods which lead to stellar mergers during the CE phases.}

% Reworked this into the paragraph above.
%\textbf{[** Might need to fact check this paragraph **] The FZ curves for ONe + X are relatively similar amongst variations beyond height, and the loss of systems is the same as described for the \kb{fiducial variation}. We have more mergers once again for $\alpha25$, which lowers the F50 curve below FZ because F50 has the shortest-ZAMS-period end that FZ does not have. $\alpha5$ and $q3$ show F50 efficiencies with a very shallow slope due to the flat orbital period distribution, as well as due to less mergers overall.}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/lisa_nums.pdf}
    \caption{The number of LISA-band systems formed for each DWD type as a function of the base-10 logarithm of metallicity, normalized to solar value. The solid line shows the FZ population with a metallicity-dependent \textbf{close} binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5. The LISA population of DWDs is dominated by stars with super-solar metallicities. This is true even for model FZ, which drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond Z$\simeq$Z$_\odot$. There is a double peak in the \textbf{fiducial and $\alpha25$} He + He populations; the first peak is caused by the sharp drop in formation efficiency past Z$\simeq$0.1$Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
    \label{fig:lisa_nums}
    \script{lisa_nums.py}
\end{figure*}

@@

\textbf{The slope of the increase for these three models is dictated by the CE efficiency $\alpha$. With increasing metallicity there is a deepening of the convective envelope of the star compared to its lower metallicity counterparts at the same point in its evolution,} %[is this the first time this idea is introduced? need to check], \KB I think this is ok!
\textbf{requiring more orbital energy to be available in order to eject the CE. Thus the high-metallicity binaries must have even wider separations for lower $\alpha$ values to ensure the binary does not merge before the envelope is ejected. We thus see a steeper separation slope for $\alpha25$, a less steep slope for $\alpha5$, and an intermediate slope for our fiducial variation which has $\alpha=1$.}

>>>>

\shorttitle{Applying a metallicity-dependent binary fraction to DWD formation}
\shortauthors{Thiele et al.}

@@

\author[0000-0001-7442-6926]{Sarah Thiele}
\affiliation{Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC, V6T 1Z1, Canada}
\affiliation{Canadian Institute for Theoretical Astrophysics, University
of Toronto, 60 St. George Street, Toronto, Ontario, M5S 1A7,
Canada}
\author[0000-0001-5228-6598]{Katelyn Breivik}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
\affiliation{Canadian Institute for Theoretical Astrophysics, University
of Toronto, 60 St. George Street, Toronto, Ontario, M5S 1A7,
Canada}
\author[0000-0003-3939-3297]{Robyn E. Sanderson}
\affiliation{Department of Physics and Astronomy, University of Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
\author[0000-0002-0296-3826]{Rodrigo Luger}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}

% Abstract with filler text
\begin{abstract}
Short-period double white dwarf (DWD) binaries will be the most prolific source of gravitational waves (GWs) for the Laser Interferometer Space Antenna (LISA). DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by overlapping GW signals, limiting the detectability of individual sources of all kinds. Population modeling of Galactic DWDs typically assumes a binary fraction of $50\%$ \textbf{and a log-uniform Zero Age Main Sequence (ZAMS) orbital period distribution}. However, recent observations have shown that the binary fraction of close, solar-type stars exhibits a strong anti-correlation with metallicity \textbf{which modulates the ZAMS orbital period distribution below $10^4$ days}. In this study we perform the first simulation of the Galactic DWD population observable by LISA which incorporates an empirically-derived metallicity-dependent binary fraction. We simulate DWDs using the binary population synthesis suite \cosmic\ and incorporate a metallicity-dependent star formation history to create a Galactic population of short-period DWDs. We compare two models: one which assumes a metallicity-dependent binary fraction \textbf{and ZAMS orbital period distribution}, and one with a binary fraction of 50\% \textbf{and log-uniform ZAMS orbital period distribution}. \textbf{We repeat our analysis for three different assumptions for Roche-lobe overflow interactions.} We find that while metallicity impacts the evolution and intrinsic properties of our simulated DWD progenitor binaries, the LISA-resolvable populations of the two models remain roughly indistinguishable. However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction \textbf{for two of our four variations.} This effect lowers the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources. \textbf{The LISA population remains unchanged in number for two variations, highlighting the sensitivity of the population to binary evolution prescriptions.}
\end{abstract}

@@

\textbf{Figure \ref{fig:met_dep_porb} shows the companion frequency f$_{\rm{logP}}$ for solar-type stars as a function of the logarithm of orbital period, mirroring the inner binaries curve of Figure 2 in \citet{Moe2021} and scaling to an overall multiplicity frequency of 0.67 (equivalent to an integrated binary fraction of 50\%) at solar metallicity. To obtain the normalization of the companion frequency for close binaries (P$_{\rm{orb}}<10^4$),} we fit the results presented in \citet{Moe2019} using linear regression to obtain a piecewise relation between the metallicity, [Fe/H] and \text{close} binary fraction $f_{\rm{b}}$ as

@@

\textbf{We count all higher-order companions as secondary, or binary, components. We show curves for all 15 of our metallicity bins, increasing in metallicity from darkest to lightest curve colour. The lowest metallicity ([Fe/H]=-2.3) shows the highest propensity for short-period binaries, in contrast to higher metallicity systems which have a frequency distribution with a relatively constant companion frequency for orbital periods between $10^4$ and $10^6$ days.}

\textbf{While we simulate binaries across the entire orbital period distribution, the close binary fraction, which exhibits the discussed metallicity dependence, will be that which impacts the LISA population since systems with $\log_{10}(\rm{P}_{\rm{orb}}/$day)$>4$ will be unlikely to evolve enough to enter the LISA band by present day.}

@@

The metallicity-dependent \textbf{close} binary fraction \textbf{for solar-type binaries (P $< 10^4$ days), or simply the close binary fraction from here on, } is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid. The \textbf{close} binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly. These two opposing trends compete throughout this study along with the impact of metallicity on single star evolution to form the final numerical distribution of systems in our DWD populations.

@@

\noindent where $h_c$ is the characteristic strain of the system, $S_n(f)$ is the LISA sensitivity curve of \citet{Robson2019}, and the frequency limits are determined by the orbital evolution over the observation time, $T_{\rm{obs}}=4\,\rm{yr}$. The characteristic strain for circular orbits is 
\begin{equation}
    h_{c}^2 = \frac{2^{2/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}},
\end{equation}
\noindent where $\mathcal{M}_c = (M_1M_2)^{3/5}/(M_1 + M_2)^{1/5}$ is the system's chirp mass, and $D_L$ is the systems luminosity distance which we assume to be the distance of each simulated DWD to the Sun.

@@

The Galactic foreground included in the \citet{Robson2019} LISA noise curve was generated using a different binary evolution code and set of model assumptions for DWD formation and evolution \citep{Toonen2012, Korol2017}. Thus, we use the detector curve only and generate an approximate foreground from each of our populations as follows. Instead of performing a full source subtraction algorithm \citep[e.g.][]{Littenberg2020}, which is out of the scope of this work, we calculate the PSD of the Galactic DWD population with a frequency resolution set by the LISA mission time as $1/T_{\rm{obs}}\sim1/4\,\rm{yr}^{-1}\sim8\times10^{-9}\,\rm{Hz}$. We then approximate the foreground as the running median of the PSD with a boxcar window with a width of $10^3$ frequency bins similar to \citet{Benacquista2006}. The Galactic DWD PSD is truncated near $10\,\rm{mHz}$ for both of our models because we remove all DWDs which experience Roche-lobe overflow. In order to smooth the effect of this truncation in our foreground, we fit each running median with fourth-order polynomials for GW frequencies up to $1\,\rm{mHz}$, thus allowing an approximation of the foreground PSD for higher frequencies. These fits are listed in Table~\ref{tbl:fits} where the polynomial is described as
\begin{equation}
\label{eq:fit}
    \log_{10}(\rm{confusion\ fit}/\rm{Hz}) = a\,x^4 + b\,x^3 + c\,x^2 + d\,x + e
\end{equation}
\noindent and $\rm{x}=\log_{10}(f_{\rm{GW}}/\rm{Hz})$. We add the fitted polynomial of the PSD's running median to the LISA noise PSD to obtain a sensitivity curve for each model \textbf{and variation}.

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/form_eff.pdf}
    \caption{The DWD formation efficiency vs metallicity of DWD populations simulated with \cosmic. Each panel shows the formation efficiency for a given DWD type \textbf{and variation}. The solid lines indicate the formation efficiency for model FZ which incorporates a metallicity-dependent binary fraction. The dashed lines indicate the formation efficiency for model F50, which assumes a constant binary fraction of $50\%$. The DWD formation efficiency drops by a factor of $4-5$ for model FZ and a factor of \textbf{1-5} for model F50. See Section~\ref{sec:formeff} for a careful description of the trends for each DWD type.}
    \label{fig:form_eff}
    \script{form_eff.py}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/CEsep.pdf}
    \caption{Average interaction separation, $\overline{\mathrm{a}}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type \textbf{and variation} from model F50. Solid lines show the average separation at the first RLO for binaries in each metallicity bin. The shaded regions show the $1\sigma$ spread around the mean within each metallicity bin. The average interaction separation increases with metallicity for every DWD type\textbf{, except for $\alpha5$ which remains approximately constant for CO + He and ONe + X}. The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts. The sharp drop of the CO + CO average at the highest-metallicity bin \textbf{of the fiducial variation} is due to binning effects of the figure: it only contains \textbf{506} systems, of which the majority stem from a single low-separation system which was sampled \textbf{468} times times during the simulation. \textbf{The regions of metallicity where there is not shading beyond the mean trend are also due to low numbers of DWDs in each bin}.} 
    \label{fig:CEsep}
    \script{CEsep.py}
\end{figure*}

For short-period CO + He DWD progenitor binaries with orbital periods below $\sim30~\rm{days}$, the only channel for \textbf{stellar} mergers before DWD formation is during a CE evolution. This channel is similar to the stellar merger channel for He + He DWDs, but due to higher-mass progenitors the CE evolution results in the binary component with a higher mass becoming a CO WD. At higher metallicities, the CO WD merges with its companion. Higher-metallicity progenitors have a larger fraction of their mass in the convective envelope when compared to lower-metallicity stars of the same mass \citep{Amard2019, Amard2020}. Thus a CE phase with a higher-metallicity progenitor requires more orbital energy to eject the common envelope, causing a larger amount of orbital shrinking which results in a merger later in its binary evolution.

For CO + He DWD progenitor systems with intermediate orbital periods ($1.5\leq \log_{10}(P_{\rm{orb}}/\rm{day})< 2.5$) the mechanisms which impact formation efficiency are complex. The dominant way to \textbf{not form} CO + He DWDs is stellar mergers that occur during the second CE phase. For lower-metallicity systems, the second CE is successful, while the opposite is true for higher-metallicity systems. This is again because the envelope mass of the CE evolution donor at higher metallicity is larger than it would be at lower metallicity and thus requires more orbital energy to eject in the CE phase. This leads to shorter post-CE orbital periods after the first CE phase and hence mergers during the second phase.

@@

\textbf{For binary systems leading to He + He DWDs, there are many more mergers for $\alpha25$ than for the fiducial variation. The lower CE efficiency leads to DWD progenitor mergers from a failed CE ejection, or the CE shrinking the orbit such that it then merges on the second CE phase. Because there are more ZAMS binaries with orbital periods shorter than $10^4$ days in F50, as the population evolves there are more likely to be binary interactions in the population for F50 than FZ. This leads to more mergers in $\alpha25$ occurring for F50 before formation of the DWD and thus a lower formation efficiency overall for F50 in contrast to FZ. This is illustrated in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}. Similar to the fiducial parameter variation, a binary that becomes a He + He DWD at lower metallicities would merge before becoming one at higher metallicities because of the longer evolution timescales. These later interactions lead to closer post-CE separations and thus more mergers. The dip at [Fe/H] $\simeq -1.5$ stems from mergers before the DWD forms, again similar to the fiducial parameter variation. The peak that occurs in $\alpha25$ at $\sim 10\%$ Z$_\odot$ arises from binaries evolving faster and thus interacting earlier as metallicity increases. This means that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive to produce a He + He DWD. At higher metallicities, there are a higher proportion of wide ZAMS binaries, which evolve off the Main Sequence too slowly to form a He + He DWD, causing the efficiency drop.}

@@

\textbf{Beyond the effects described above, the efficiency drop across metallicity is similar to the fiducial parameter variation in that it depends on the metallicity-dependent ZAMS orbital period distribution emphasizing short-period systems at low metallicities, and on the change of formation channel for different period ranges across metallicity. We find the highest formation efficiency for variation $q3$. Only the shortest-period binaries do not form a DWD through mergers at higher metallicities. At low metallicities, even binaries with ZAMS orbital periods P$_{\rm{orb}}\lesssim 100$ days form He + He DWDs, with binaries in model FZ reaching ZAMS orbital periods less than a day in length. This leads to a higher formation efficiency from F50 over FZ for parameter variation $q3$ because of the higher number of shortest-period ZAMS binaries in the log-uniform distribution of F50.}

\textbf{For CO + He binaries, there are again many more mergers for parameter variation $\alpha25$ relative to the fiducial case. This is the dominant way that progenitors do not evolve to produce DWDs at higher metallicities. At low metallicities, a number of progenitor binaries form CO + CO DWDs instead of He + CO DWDs. This is especially the case near $\log_{10}$(Z/Z$_\odot)\sim -2$, where RLO occurs late enough in a binary's evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence producing a dip in the formation efficiency. Because parameter variation $\alpha5$ leads to less mergers due to the high CE efficiency, the formation efficiency is mostly governed by the metallicity-dependent ZAMS orbital period distribution. At higher metallicities, the majority of cases in model FZ where progenitors don't produce a CO + He DWD are from progenitor mergers or from He + He DWDs forming instead of CO + He DWDs. At higher metallicities, the ZAMS orbital period distribution of FZ also drops below that of F50 and extends out to orbital periods beyond what would form a CO + He. This causes the formation efficiencies for FZ and F50 to cross at log$_{10}$(Z/Z$_\odot$)$\sim-0.5$. This is also apparent for the $q3$ variation, and to a lesser extent in the fiducial case. In $q3$, for any given orbital period we find that lower mass DWDs originate from lower metallicities, thus leading to an approximately constant formation efficiency.}

\textbf{For CO + CO, across all variations, very close ZAMS binaries (P$_{\rm{orb}}\sim\mathcal{O}(100$ days)) at high metallicities form a CO + He or He + He DWD instead of a CO + CO because the binary interacts before core Helium burning of one or both components. There are again many more mergers in $\alpha25$, and fewer mergers for $\alpha5$. Due to the high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods survive to become CO + CO DWDs rather than merging or becoming CO + He or He + He DWDs. There are less fewer mergers overall for $q3$ than all the $\alpha$ variations because the first RLO occurrence leads to stable mass transfer from the primary to the secondary rather than multiple CE phases. For both the $\alpha5$ and $q3$ variations, the majority of CO + CO DWDs originate in wide enough orbits that they don't interact before DWD formation. This leads to an approximately constant formation efficiency across metallicity in both cases.}

\textbf{For model FZ, the ONe + X formation efficiencies follow similar trends aross each parameter variation. Their formation scenarios are similar to those described above for ONe + X DWDs in the fiducial binary evolution parameter set. The main difference between each parameter variation is only in the number of sources produced since the number of stellar mergers that occur before DWD formation increases with decreasing common envelope efficiency. In model F50, the formation efficiency is decreased significantly for parameter variation $\alpha25$ because the log-uniform orbital period distribution produces many ZAMS binaries with very short orbital periods which lead to stellar mergers during the CE phases.}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/lisa_nums.pdf}
    \caption{The number of LISA-band systems formed for each DWD type \textbf{and parameter variation} as a function of the base-10 logarithm of metallicity, normalized to solar value. The solid line shows the FZ population with a metallicity-dependent \textbf{close} binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5. The LISA population of DWDs is dominated by stars with super-solar metallicities. This is true even for model FZ, which drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond Z$\simeq$Z$_\odot$. There is a double peak in the \textbf{fiducial and $\alpha25$} He + He populations; the first peak is caused by the sharp drop in formation efficiency past $\rm{Z}\simeq0.1 \rm{Z}_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
    \label{fig:lisa_nums}
    \script{lisa_nums.py}
\end{figure*}

@@

\textbf{The slope of the increase for these three models is dictated by the CE efficiency $\alpha$. With increasing metallicity there is a deepening of the convective envelope of the star compared to its lower metallicity counterparts at the same point in its evolution, requiring more orbital energy to be available in order to eject the CE. Thus the high-metallicity binaries must have even wider separations for lower $\alpha$ values to ensure the binary does not merge before the envelope is ejected. We therefore see a steeper separation slope for $\alpha25$, a less steep slope for $\alpha5$, and an intermediate slope for our fiducial variation which has $\alpha=1$.}

\textbf{The DWDs in model $q3$ that survive into the LISA band at present day have different formation channels than those of our other three parameter variations. Most importantly, in contrast to two CE phases for the fiducial, $\alpha25$ and $\alpha5$ parameter variations, the DWD progenitors in parameter variation $q3$ typically undergo a phase of stable mass transfer as the binary's first interaction. During mass transfer the orbit first shrinks, and then will slightly widen once the binary's mass ratio flips. This process leads to formation of the first WD component. The companion is then formed later in the binary's evolution through a CE phase. We show the CE phase which results from the second interaction for parameter variation $q3$ in Figure \ref{fig:CEsep}.}
